Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2018-12-19 paper/ms.tex
Add zmax to text
Add text to describe many orbit fig

First, we illustrate the time-dependence of one possible inaccurate reference
frame. We begin by taking an orbit with initial position $(8, 0, 0)\,\kpc$ and
initial velocity $(0, -190, 50)\,\kms$ --- this corresponds to an orbit with
actions $(J_r, L_z, J_z) = (32.5, -1520, 23.0)\,\actunit$. The orbit is
plotted in \Gus{Appendix x}. We then suppose that an observer makes
observations of this orbit in a coordinate system that is incorrect in radius by
$200\,\pc$ and height by $100\,\pc$ --- we subtract the vector $(200, 0,
100)\,\pc$ from each position in the orbit. This corresponds to an observer
physically located at the position $(8, 0, 0)\,\kpc$ but erroneously thinking
they are located at $(8.2, 0, 0.1)\,\kpc$.

@@

We now repeat the procedure but continuously changing the error in the assumed
midplane. In Figure~\ref{fig:many_orbit_wrong_ref}, we report the 95\uth minus
5\uth percentile divided by the true action value for three different orbits.
The red orbit is exactly the same as in Figure~\ref{fig:one_orbit_wrong_ref},
and we also consider two more planar orbits with initial vertical velocities
of $30\,\kms$ (\Gus{orange}) and $10\,\kms$ (\Gus{blue}). For these two new
orbits, the true actions are $(J_r, L_z, J_z) = (37.9, -1520, 7.0)\,\actunit$
and $(40.4, -1520, 0.7)\,\actunit$ for the \Gus{orange} and \Gus{blue} orbits,
respectively. \Gus{Easy way to explain change in $J_r$?}

>>>>

First, we illustrate the time-dependence of one possible inaccurate reference
frame. We begin by taking an orbit with initial position $(8, 0, 0)\,\kpc$ and
initial velocity $(0, -190, 50)\,\kms$ --- this corresponds to an orbit with
actions $(J_r, L_z, J_z) = (32.5, -1520, 23.0)\,\actunit$. The orbit is
plotted in \Gus{Appendix x}. For reference, the $z_{\text{max}}$ for this
orbit is $854\,\pc$. We then suppose that an observer makes observations of
this orbit in a coordinate system that is incorrect in radius by $200\,\pc$
and height by $100\,\pc$ --- we subtract the vector $(200, 0, 100)\,\pc$ from
each position in the orbit. This corresponds to an observer physically located
at the position $(8, 0, 0)\,\kpc$ but erroneously thinking they are located at
$(8.2, 0, 0.1)\,\kpc$.

@@

We now repeat the procedure but continuously changing the error in the assumed
midplane. In Figure~\ref{fig:many_orbit_wrong_ref}, we report the 95\uth minus
5\uth percentile divided by the true action value for three different orbits.
The red orbit is exactly the same as in Figure~\ref{fig:one_orbit_wrong_ref},
and we also consider two more planar orbits with initial vertical velocities
of $30\,\kms$ (\Gus{orange}) and $10\,\kms$ (\Gus{blue}). For these two new
orbits, the true actions are $(J_r, L_z, J_z) = (37.9, -1520, 7.0)\,\actunit$
and $(40.4, -1520, 0.7)\,\actunit$ for the \Gus{orange} and \Gus{blue} orbits,
respectively. The value of $z_{\text{max}}$ for these orbits are $122\,\pc$
and $425\,\pc$, respectively (with the blue orbit having $z_{\text{max}}$ of
$854\,\pc$.) \Gus{Easy way to explain change in $J_r$?}

The top row of Figure~\ref{Fig:many_orbit_wrong_ref} shows the error in each
action assuming an offset in the midplane. In the {\em bottom row} we also
consider offsets in the Galactocentric radius $R$. The {\em left}, {\em
middle}, and {\em right} columns show the 95\uth minus 5\uth percentile of the
measured action over the course of the incorrect orbit divided by the true
action value as a percentage.

In the {\em upper middle} panel, there is essentially no error in the
determination of $L_z$. This is expected since, in principle, $L_z$ only
depends on the $x$- and $y$-components of the position and velocity of the
stars\footnote{Though this is not how we compute $L_z$ in practice.}, and is
thus unaffected by offsets in $z$.

The {\em upper right} panel shows that the fractional error in $J_z$ is more
exaggerated for more planar orbits. For the nearly planar (blue) orbit,
deviations that are $\sim30\,\pc$ already give $100\%$ deviations in the
actions. The required offset for $100\%$ deviation is $\sim120$ and
$\sim225\,\pc$ for the orange and red orbits, respectively. \Gus{Make these
numbers exact.}

For completeness, we also consider the effect of offsets in the Galactocentric
radius $R$ in the {\em bottom panels}. The error is largest for $J_r$, with
some deviations resulting in $L_z$ and relatively small deviations in $J_z$.
In the {\em bottom left} panel the orange and blue lines overlap, and in the
{\em bottom middle} and {\em bottom right} panels all three lines overlap.
